---
title: styler 1.1.0
author: Lorenz Walthert
date: '2018-11-21'
categories:
  - R
tags:
  - packages
  - styler
description: styler gains syntax highlighting, can style Rnw files, roxygen
  code examples and more in version 1.1.0.
slug: styler-v1.1.0
comments: true
---

[styler](https://github.com/r-lib/styler) 1.1.0 is now available on CRAN. This 
release introduces new features and is fully backward-compatible. It also
adapts to changes in the R parser committed into R devel ([#419](https://github.com/r-lib/styler/issues/419)). Major changes
are:

* styler can now style roxygen code examples in the source code of package.
  This might be helpful for package developers. The option is enabled by
  default, so you have to explicitly turn it off if you want styler to leave
  the code examples as is: 

```{r, eval = FALSE}
styler::style_pkg(include_roxygen_examples = FALSE)
```
  
  
* In addition to R and Rmd files, styler can now handle Rnw files too. The API 
  ignores capitalization and dot-prefixing for file types:

```{r, eval = FALSE}
styler::style_dir(filetype = c("r", "Rmd", ".rnw"))
```
* the print method for the output of `style_text()` (`print.vertical()`) now
  returns syntax-highlighted code by default, controllable via the option 
  `styler.colored_print.vertical` using the [prettycode](https://CRAN.R-project.org/package=prettycode) package. This only 
  works when ran in a console though, so you can c/p this snippet into yours
  to see how it works:
  
```{r, echo = TRUE, results = FALSE}
styler::style_text(c(
  "add <- function(...) {", 
  "purrr::reduce(list(...), `+`)", 
  "}"
))
```


There were also quite a few minor changes, the most visible ones to the user 
were a complete re-design of the README and the fact that the cursor position is 
now remembered for styling via Addin. For details, you can have a look at the [release notes](https://github.com/r-lib/styler/releases/tag/v1.1.0) or check the 
full [commit history](https://github.com/r-lib/styler).


Thanks to all contributors for patches, issues and the like:
@jonmcalder, @krlmlr, @IndrajeetPatil, @kalibera, @Hasnep, @kiranmaiganji, 
@dirkschumacher, @ClaytonJY, @wlandau, @maurolepore.

Although not directly related to this release, we would like to highlight that 
the functionality of styler is also available in other packages:

  - `usethis::use_tidy_style()` styles your project according to the
    tidyverse style guide.
  - `reprex::reprex(..., style = TRUE)` to prettify reprex code before
    printing. To permanently use `style = TRUE` without specifying it
    every time, you can add the following line to your `.Rprofile` (via
    `usethis::edit_r_profile()`): `options(reprex.styler = TRUE)`.
  - you can pretty-print your R code in RMarkdown reports without having
    styler modifying the source. This feature is implemented as a code
    chunk option in knitr. use `tidy = "styler"` in the header of a code
    chunks (e.g. ` ```{r name-of-the-chunk, tidy = "styler"}`), or
    `knitr::opts_chunk$set(tidy = "styler")` at the top of your
    RMarkdown script. This feature requires the devel version of knitr.
  - pretty-printing of [drake](https://github.com/ropensci/drake)
    workflow data frames with `drake::drake_plan_source()`.

For a complete walk-through we recommend to have a look at the [initial blog post](https://lorenzwalthert.netlify.com/posts/stylerpost/) that introduces 
styler.
